RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-07-31 manuscripts/manuscript.Rmd
Improve explanation of XML vocab #79 and namespaces #80 lines 565-600

So far our examples have relied on functions that have a built-in
understanding of the kind of metadata being provided, and can thus
generate the appropriate metadata with little further guidance.
In order to be machine-readable and understandable, NeXML requires
all metadata annotations follow the RDFa format (see @Vos_2012) which
explicitly declares the meaning of the annotation. For instance, the title we gave to the `bird.orders`
phylogeny appears in the NeXML file as:

@@

We see the title appears as the value of the `content` attribute of this `meta` element.
The `id` attribute provides us with a unique way to refer to this meta
element in this document.  The `datatype` tells us that the content
is a text string (as opposed to, say, a numerical or boolean value).
The `property` is the attribute that most interests us here; it tells us
that the content is a title.  The prefix `dc` indicates the vocabulary
(here identified as an XML namespace) to which the word `title` belongs.  The prefix
is defined elsewhere in the NeXML file, as we can see with:

>>>>

So far our examples have relied on functions that have a built-in
understanding of the kind of metadata being provided, and can thus
generate the appropriate metadata with little further guidance.
In order to be machine-readable and understandable, NeXML requires
all metadata annotations follow the RDFa format (see @Vos_2012) which
explicitly declares the meaning of the annotation.

Some basic definitions about the XML syntax used to express NeXML
will be helpful for this discussion, though a more comprehensive 
introduction can be found in @Vos_2012.  For instance, consider how
the title we gave to the `bird.orders` phylogeny appears in the NeXML file
using the XML format:

@@

The format begins with an XML "tag" and the name "meta", indicated by the opening
angle bracket; `<meta`.  A closing tag `\>` indicates the end of this
XML "element" .  This tag contains several "attributes", named "id",
"property", etc., that an R user can think of as names in a `list`. What
follows the equals sign after the attribute name is called the attribute "value",
(e.g. the `id` attribute has value "m2").

The name of any element (like "meta") or attribute (like "id") in XML must be associated
with a particular dictionary called a "namespace" and specified using a "prefix"
of an abbreviation followed by a colon appearing before the name.  If no prefix
is given, as is the case for all attributes here: `id`, `property`, `datatype`,
and `content`, then a default prefix specified at the beginning of the document applies,
in this case, the NeXML namespace.  This allows users to combine different XML
that have different definitions of terms like `id` or `property`.

The example element above also uses namespaces on some of the attribute values themselves.
This is a consequence of RDFa annotation, and not strictly part of XML, though
it works much the same way.  While we hope the following examples will make these
concepts clearer, users do not need to understand XML and namespaces to use most
of the basic annotation features provided by `RNeXML`.

So much for the structure; we can now briefly explain the meaning of this element. 
We see the title appears as the value of the `content` attribute of this `meta` element.
The `id` attribute provides us with a unique way to refer to this meta
element in this document.  The `datatype` tells us that the content
is a text string (as opposed to, say, a numerical or boolean value).
The `property` is the attribute that most interests us here; it tells us
that the content is a title.  The prefix `dc` indicates the vocabulary
(here identified as an XML namespace) to which the word `title` belongs.  The prefix
is defined elsewhere in the NeXML file, as we can see with:
